\section{Employment}

\cventry{Feb 2022--Current}{Engineering Manager (Cloud Platform Team)}{Snapp!}{Tehran, Iran}{}{
	\begin{itemize}
		\item Led the design and implementation of a scalable, microservice-based architecture for a delivery industry application,
		      using \httpslink[\textbf{NATS}]{nats.io} as the primary message-passing system for more than 125 clients and delivering
		      more that 300k messages per second.
		\item Setup \textbf{Machine learning pipelines} using classical and neural network algorithms on \textbf{Kubernetes}
		      to reduce resource usage and increase the data gathering by 10\%.
		\item Lunch Kubernetes pods periodically using \httpslink[\textbf{Airflow}]{airflow.apache.org} for data processing.
		\item Setup \httpslink[\textbf{Seldon}]{www.seldon.io} for Data science team so they can serve their models
		      easily and without getting help from Dev team.
		\item Write data ingestion pipelines using \textbf{Apache Spark} and \textbf{Apache Beam} in Java.
		\item Deploy Kafka on Kubernetes using \httpslink[\textbf{Strimzi}]{https://strimzi.io/}.
		\item Mentoring teams for effective use of NATS and other messaging systems.
	\end{itemize}
}

\cventry{Oct 2020--Feb 2022}{Senior Software Engineer (Dispatching Team)}{Snapp!}{Tehran, Iran}{}{
	\begin{itemize}
		\item Built and maintained automated testing frameworks to ensure code quality and reliability,
		      and implemented CI/CD pipelines to streamline deployment and delivery processes.
		\item Devised an in-house \textbf{MQTT} load testing tool to support cluster capacity planning and stress testing.
		\item Offer an authentication and authorization solution for \textbf{EMQ} that is both highly customizable and performant.
		\item Deploy RabbitMQ, Redis on Kubernetes using their \textbf{CRD} and \textbf{operators}.
		\item Use GitOps based on \httpslink[\textbf{ArgoCD}]{argo-cd.readthedocs.io/en/stable}, so we can keep tracking the helm charts' values files.
		\item Designed and optimized databases using \textbf{PostgreSQL} and \textbf{MongoDB},
		      and implemented monitoring and alerting systems for real-time application observability using \textbf{OpenTelemetry}.
		\item To improve the response time of chat messages stored in \textbf{MongoDB}, shard the database to achieve a 50\% reduction in response time.
		\item \textbf{Mentored} and coached junior engineers on best practices for backend development
		\item Demonstrated a passion for technology and a positive approach to work,
		      while maintaining strong communication and collaboration skills with engineering
		      and non-engineering stakeholders alike.
	\end{itemize}
}

\cventry{Jan 2019--Oct 2020}{Software Engineer (Shared Services Team)}{Snapp!}{Tehran, Iran}{}{
	\begin{itemize}
		\item Optimized critical legacy applications (written in PHP) by migrating them to a modern platform and cloud infrastructure,
		      increasing availability by 20\% and facilitating faster rollout of new functionalities.
		\item Developed a \textbf{real-time stream processing} service to dynamically adjust pricing and balance demand and supply,
		      resulting in a 5\% increase in the number of accepted rides.
		\item Developed and maintained backend services in \textbf{Golang} to ensure
		      high \textbf{performance} and \textbf{reliability} for real-time order processing and \textbf{delivery tracking},
		      and engineered a suite of \textbf{microservices} to enable real-time \textbf{geofencing} and in-memory geospatial
		      indexing using \httpslink[\textbf{Tile38}]{tile38.com} with \textbf{sub-millisecond} response times.
	\end{itemize}
}

\cventry{Jan 2017--Jan 2019}{Software Architect}{IoT Working Group of Amirkabir University of Technology}{Tehran, Iran}{}{
	\begin{itemize}
		\item Introduced and extends the open-source \textbf{IoT platform Mainflux} to build a scalable and secure backend
		      infrastructure for a high-quality, end-to-end environmental monitoring product.
		\item Write the open-source \httpslink[\textbf{IoT platform I1820}]{github.com/I1820/} to use in the resource constrained environments.
		\item Worked with the backend team to design and develop a comprehensive IoT platform that manages things with multiple network protocols,
		      including wireless protocols such as \textbf{nRF}, \textbf{Zigbee}, and \textbf{LoRaWAN}.
		\item Designing a \textbf{reliable transport layer} over \textbf{NRF} to create cheap home automation systems.
		\item Developed applications for Arduino boards using \textbf{C++}.
		\item Developed \textbf{microservices} in \textbf{Python} and \textbf{Golang} to integrate sensors, actuators and gateways with the IoT platforms.
		\item Collaborated closely with hardware engineers to ensure seamless communication between the IoT
		      platform and the sensors and actuators.
		\item Designed and implemented \textbf{RESTful} APIs and \textbf{messaging protocols} to
		      enable communication between microservices.
		\item \textbf{Communicated} effectively with stakeholders, including project managers, product owners, and clients,
		      to ensure alignment and transparency of project goals, progress, and outcomes.
		\item Designed and implemented an \textbf{Angular}-based admin panel for an IoT client,
		      integrating \httpslink[\textbf{leaflet}]{leafletjs.com} to display sensor locations and data.
		      Utilized best practices in frontend development, including responsive design and cross-browser compatibility, to deliver a high-quality and user-friendly experience.
		\item Developed time series plots and diagrams using \textbf{charts.js} to visualize data for another IoT client,
		      delivering a comprehensive and insightful dashboard for data analysis and decision-making.
		\item Maintained up-to-date knowledge of the latest technologies and tools in the Python,
		      Golang, and IoT ecosystems, and incorporated them into the development process to improve efficiency and performance.
		\item Utilized best practices in software engineering, including code reviews, testing, and continuous
		      integration and deployment, to deliver high-quality and robust code.
		\item Mentored junior students and provided guidance on technical issues,
		      design patterns, and software architecture.
	\end{itemize}
}

\cventry{Jul 2013--Mar 2017}{Software Engineer}{Nahalco}{Tehran, Iran}{}{
	\begin{itemize}
		\item Setup company website on \textbf{JAM Stack} using GitHub pages and Jekyll.
		\item Write different types of \textbf{scrappers} to scrape live cryptocurrency information from websites in Python.
		\item Use \textbf{serverless-like} architecture to run scrappers periodically on \textbf{Docker swarm} infrastructure.
		\item Provide a data-processing pipeline using \textbf{Apache Spark} to ingest the stock information.
		\item Design and implement the IoT platform which provides a comprehensive solution for farmers to meticulously track their crops'
		      development and understand their specific needs.
		\item Use \textbf{Sentinel-II satellite imagery} to offer insights into the vitality and health of crops,
		      allowing for timely interventions.
	\end{itemize}
}

\cventry{Jan 2016--Jan 2017}{Software Engineer}{Computer \& Information Center of Amirkabir University of Technology}{Tehran, Iran}{}{
	\begin{itemize}
		\item Led the development of a \httpslink[\textbf{metering internet system}]{github.com/aut-cic/internet} using \httpslink[FreeRADIUS]{freeradius.org/} and Python,
		      enabling API calls to the FreeRADIUS system to display usage's volumes.
		      Utilized best practices in Python development, including modular design and asynchronous programming,
		      to deliver a scalable and efficient system.
	\end{itemize}
}

\cventry{Jun 2014--May 2016}{Software Engineer}{Avidnet}{Tehran, Iran}{}{
	\begin{itemize}
		\item Achieved in-application video call solution using \textbf{WebRTC} based on \textbf{Pion}
		      Framework which \textbf{increased application installation rate by 5\%} and can
		      handle \textbf{1K concurrent calls} on distributed design.
		\item Proceed with the installation and configuration of two HPE ProLiant DL380 Gen9 servers,
		      ensuring \textbf{VMware ESXi} is properly set up on both.
		\item Deploy services using \textbf{Docker Swarm} over staging and production environment.
		\item Setup \textbf{CI/CD} pipeline using \textbf{TravisCI} to lint and build services.
	\end{itemize}
}
