\section{Work Experience}

\cventry{2016}{Intern}{Iranian Telecommunication Reseach Center}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Collaborated with three colleagues to design and implement innovative home automation solutions leveraging the Raspberry Pi and ThingSpeak.
    \item Utilized our expertise in Ruby programming to effectively maintain and optimize the ThingSpeak platform for seamless integration with our IoT System.
    \item As a resutlt, we were able to achieve significant improvements in home automation performance, efficiency, and functionality.
  \end{itemize}
}

\cventry{2017--2019}{System Architect}{IoT Working Group of Amirkabir University of Technology}{Tehran, Iran}{}{%
}

\cventry{2019--current}{Engineering Manager}{Snapp!}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Developed location based systems using Golang that handle heavy load as a Charlie team member.
      We read location data which was almost 10,11K at that time and process them using Golang and stored results into
      location-based cache named \httpslink[tile38](https://github.com/tile38).
    \item Designed and developed surge pricing system that consumes more than 6K messages per second with Golang as a Shared Service team member.
    \item Designed and developed event dispatching services based on polling and MQTT as a Dispatching team member.
    \item Deploy and maitain heavy load services on kubernetes.
    \item Team lead of a cross-functional team which has 9-12 members.
  \end{itemize}
}
